\documentclass[11pt]{scrartcl}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\begin{document}

This question involves the use of simple linear regression on the Auto data set.

\begin{itemize}
\item Use the \texttt{lm()} function to perform a simple linear regression with mpg as the
response and horsepower as the predictor. Use the \texttt{summary()} function to
print the results. Comment on the output. For example:
\begin{enumerate}
\item Is there a relationship between the predictor and the response?
\item How strong is the relationship between the predictor and the response?
\item Is the relationship between the predictor and the response positive or
negative?
\item What is the predicted mpg associated with a horsepower of 98? What are the
associated 95 percent conﬁdence and prediction intervals?
\end{enumerate}
\item Plot the response and the predictor. Use the \texttt{abline()} function to display
the least squares regression line.
\item Use the \texttt{plot()} function to produce diagnostic plots of the least squares
regression ﬁt. Comment on any problems you see with the ﬁt.
\end{itemize}

This question involves the use of multiple linear regression on the Auto data
set.

\begin{itemize}
\item Produce a scatterplot matrix which includes all of the variables in the data
set.
\item Compute the matrix of correlations between the variables using the function
\texttt{cor()}. You will need to exclude the name variable, \texttt{cor()} which is
qualitative.
\item Use the \texttt{lm()} function to perform a multiple linear regression with mpg as
the response and all other variables except name as the predictors. Use the
\texttt{summary()} function to print the results. Comment on the output. For
instance:
\begin{enumerate}
\item Is there a relationship between the predictors and the response?
\item Which predictors appear to have a statistically signiﬁcant relationship to
the response?
\item What does the coeﬃcient for the year variable suggest?
\end{enumerate}
\item Use the \texttt{plot()} function to produce diagnostic plots of the linear regression
ﬁt. Comment on any problems you see with the ﬁt. Do the residual plots suggest
any unusually large outliers? Does the leverage plot identify any observations
with unusually high leverage?
\item Use the \texttt{*} and \texttt{:} symbols to ﬁt linear regression models with interaction
eﬀects. Do any interactions appear to be statistically signiﬁcant?
\item Try a few diﬀerent transformations of the variables, such as \(\log{X}\),
\(\sqrt{X}\) and \(X^{2}\). Comment on your findings.
\end{itemize}
\end{document}